Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-04-02 PandaEvolution.tex
Address Jack's comments #10

Backfill availability is typically a small fraction of the total capacity  of
a resource. Notwithstanding,  given the size of Titan this translates into a
substantial capacity. Every year, about 10\% of Titan's capacity remains
unused, corresponding to an average of 30,000 unused cores. This equals
approximately 270M core hours per year, roughly 30\% of the overall capacity
of WLCG.

>>>>

Backfill availability is typically a small fraction of the total capacity  of a
resource. Notwithstanding,  given the size of Titan this translates into a
substantial capacity. Every year, about 10\% of Titan's capacity remains
unused~\cite{barker2016us}, corresponding to an average of 30,000 unused cores.
This equals approximately 270M core hours per year, roughly 10\% of the overall
capacity of WLCG.

### 2017-04-02 PandaOverview.tex
Address Jack's comments #10

Pilot-enabled WMS enable high throughput of tasks execution while supporting
interoperability across multiple sites. This is particularly relevant for LHC
experiments, where millions of tasks are executed across multiple sites every
month, analyzing and producing petabytes of data. The design of PanDA WMS
started in 2005 and its implementation went into production for the LHC Run 1 on
2009. PanDA was then extended with new subsystems to be deployed on Run 2, on
2015.

>>>>

Pilot-capable WMS enable high throughput of tasks execution while supporting
interoperability across multiple sites. This is particularly relevant for LHC
experiments, where millions of tasks are executed across multiple sites every
month, analyzing and producing petabytes of data. The design of PanDA WMS
started in 2005 to support ATLAS, one of the LHC experiments. PanDA went into
production for the LHC Run 1 on 2009, and was then extended with new subsystems
to be deployed on Run 2, on 2015.
